A Model for Extracting Time Delays from Noisy Time Series Data

### 2013-08-16 doc/Paper1/ms.tex
Table of variables

\newcommand{\params}{\boldsymbol{\theta}}
\newcommand{\data}{\boldsymbol{D}}

@@

\section{Bayesian Inference}
For inferring unknown parameters $\params$ from data $\data$,
Bayes' rule gives the posterior distribution
\begin{eqnarray}
p(\params | \data) \propto p(\params)p(\data|\params)
\end{eqnarray}
The prior distribution $p(\params)$ describes prior knowledge or uncertainty
about the values of the parameter(s). The ``sampling distributions''
$p(\data|\params)$
describes prior knowledge about the data we expect to observe, as a function of
$\params$ (Caticha). When $\data$ is fixed $p(\data|\params)$ is a function of
$\params$ only and is called the likelihood function.

@@

>>>>

\newcommand{\params}{\boldsymbol{\theta}}
\newcommand{\data}{\boldsymbol{D}}
\newcommand{\info}{\boldsymbol{I}}

@@

\section{Bayesian Inference}
For inferring unknown parameters $\params$ from data $\data$ in the context
of prior information $\info$,
Bayes' rule gives the posterior distribution
\begin{eqnarray}
p(\params | \data, \info) \propto p(\params|\info)p(\data|\params, \info)
\end{eqnarray}
The prior distribution $p(\params|\info)$ describes prior knowledge or uncertainty
about the values of the parameter(s). The ``sampling distributions''
$p(\data|\params,\info)$
describes prior knowledge about the data we expect to observe, as a function of
$\params$ (Caticha). When $\data$ is fixed $p(\data|\params,\info)$ is a function of
$\params$ only and is called the likelihood function.

@@

\begin{table*}
\begin{tabular}{lll}
\hline
{\bf Parameter} &	{\bf Meaning}			& {\bf Prior}\\
\hline
$\tau_2$	&	Time delay relative to image 1	& Cauchy()$T(,)$\\
$\{m_1, m_2\}$	&	Mean magnitude for each image	& Uniform()\\
\hline
{\bf Data}	&	{\bf Meaning}			& {\bf Sampling Distribution}\\
\hline
$\{Y_1, ..., Y_N\}$ &	Noisy magnitude measurements	& $\mathcal{N}\left(\mathbf{m}(\params), \mathbf{C}(\params)\right)$\\
\hline
{\bf Prior Information} & {\bf Meaning}			&\\
\hline
$N$		&	Number of measurements (all images together)\\
$\{t_1, ..., t_N\}$ &	Measurement times\\
$\{k_1, ..., k_N\}$ &	Flags identifying which image was observed
\end{tabular}
\end{table*}
